\section{Introduction \& Motivations}

% G1: 1995: prob facts and rules
% G2: 2000: + assumptions, _tie/_untie (_pri)
% G3: 2001: + specials (_stem, _soundex, _eq, ...)
% G4: 2002: + relational Bayes
% G5: 2004: + top-k and _sort
% G6: 2006: + Ratio Join, LM, BM25-TF
% G7: 2009: + _poisson etc: 
% G8: 2010: + range atoms, $0
% G9: 2012: + functions (e.g. avg, sum)


Ten generations:

\begin{description}
\item[G1: 1995]
	Probabilistic facts and rules:
	Intensional semantics: Disjointness key, event expressions.
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G2: 2000]
	Extenisonal semantics:
	Assumptions for specifying probability aggregation.
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G3: 2001]
	Special predicates: stemming, soundex, etc
	Plug-ins / hooks.
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G4: 2002]
	The relational Bayes, conditional atoms.
	Expressiveness to describe conditional probabilities.
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G5: 2004]
	top-k and semi-sorted streams; window-based processing.
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G6: 2006]
	Ratio join
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G7: 2009]
	Probability distributions functions, e.g.~\_poisson(Avg,K).
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G8: 2010]
	Range atoms. Reasoning over probabilities (\$0 attribute).
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G9: 2012]
	Functions.
\inputHySpiritProgram{examples/generation-1}{pd}

\item[G10: 2014]
	Modelling dependencies between event occurrences
\inputHySpiritProgram{examples/generation-1}{pd}

\end{description}


\subsection{Structure \& Contributions}

\section{Ten Generations}

\subsection{G1 1995: Prob.~Facts and Rules}
\input{Syntax/generation-1}

Intermediates: FVPD and POOL.

\subsection{G2 2000: Probabilistic Assumptions}
\input{Syntax/generation-2}

\subsection{G3 2001: Special Predicates}
\input{Syntax/generation-3}

\subsection{G4 2002: Relational Bayes}
\input{Syntax/generation-4}

\subsection{G5 2004: Top-K}
\input{Syntax/generation-5}

\subsection{G6 2006: Ratio Join}
\input{Syntax/generation-6}

\subsection{G7 2009: Distribution Predicates}
\input{Syntax/generation-7}

\subsection{G8 2010: Range Atoms}
\input{Syntax/generation-8}

\subsection{G9 2012: Functions}
\input{Syntax/generation-9}

\subsection{G10 2014: Dependencies}
\input{Syntax/generation-10}

\section{Background}

\section{Summary \& Conclusions}
